---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Mapping the Evidence Gaps for Stroke in Lower-Middle Income Countries (LMIC) and Low Income Countries (LIC)

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![test targets workflow](https://github.com/OxfordIHTM/stroke-lmic-review/actions/workflows/test-targets-workflow.yml/badge.svg)](https://github.com/OxfordIHTM/stroke-lmic-review/actions/workflows/test-targets-workflow.yml)
<!-- badges: end -->

This repository is a [`docker`](https://www.docker.com/get-started)-containerised, [`{targets}`](https://docs.ropensci.org/targets/)-based, [`{renv}`](https://rstudio.github.io/renv/articles/renv.html)-enabled [`R`](https://cran.r-project.org/) workflow for a project on mapping the evidence gaps for stroke in low and middle-income countries.

## About the Project

The burden of stroke is among the top five causes of mortality and morbidity in low-middle income countries (LMICs) and low income countries (LICs) and this burden is growing, yet evidence on contributing causes and the efficacy of interventions appears to be disproportionately generated in high-income settings for discrete population groups. This review maps existing evidence drawing on LMIC and LIC populations.  

## Repository Structure

The project repository is structured as follows:

```
stroke-lmic-review
    |-- .github/
    |-- data/
    |-- data-raw/
    |-- outputs/
    |-- R/
    |-- reports
    |-- renv
    |-- renv.lock
    |-- .Rprofile
    |-- packages.R
    |-- _targets.R
```

* `.github` contains project testing and automated deployment of outputs workflows via continuous integration and continuous deployment (CI/CD) using Github Actions.

* `data/` contains intermediate and final data outputs produced by the workflow.

* `data-raw/` contains raw datasets, usually either downloaded from source or added manually, that are used in the project.

* `outputs/` contains compiled reports and figures produced by the workflow.

* `R/` contains functions developed/created specifically for use in this workflow.

* `reports/` contains literate code for R Markdown and/or Quarto reports rendered in the workflow.

* `renv/` contains `renv` package specific files and directories used by the package for maintaining R package dependencies within the project. The directory `renv/library`, is a library that contains all packages currently used by the project. This directory, and all files and sub-directories within it, are all generated and managed by the `renv` package. Users should not change/edit these manually.

* `renv.lock` file is the `renv` lockfile which records enough metadata about every package used in this project that it can be re-installed on a new machine. This file is generated by the `renv` package and should not be changed/edited manually.

* `.Rprofile` file is a project R profile generated when initiating `renv` for the first time. This file is run automatically every time R is run within this project, and `renv` uses it to configure the R session to use the `renv` project library.

* `packages.R` file lists out all R package dependencies required by the workflow.

* `_targets.R` file defines the steps in the workflow's data ingest, data processing, data analysis, and reporting pipeline.

## Reproducibility

### R version

This project is built using `R 4.6.0`. To manage R versions, it is recommended to use [`rig`](https://github.com/r-lib/rig) - an R installation manager - to be able to install multiple versions of R and switch between them as needed.

### R package dependencies

This project uses the `{renv}` framework to record R package dependencies and versions. Packages and versions used are recorded in `renv.lock` and code used to manage dependencies is in the `renv` directory and other files in the root project directory.

On starting an R session in the working directory of this repository, first run 

```R
renv::restore()
```

to install R package dependencies. This is only done once when the project is being initiated for the first time by a user.

### Encryption

This project uses encrypted environment variables and authentication keys used to authenticate with the different services used by the project. These services include:

* Large language models (LLMs) provided by [OpenAI](https://chatgpt.com/), [Anthropic](https://claude.ai/new), and [Google](https://gemini.google.com/); and,

* [Sheets](https://sheets.google.com), [Drive](https://drive.google.com), and [Gmail](https://mail.google.com) services provided by [Google](https://www.google.com).

Encryption is managed using [`git-crypt`](https://github.com/AGWA/git-crypt). Collaborators will need to [install `git-crypt`](https://github.com/AGWA/git-crypt) and then provide their GPG key to the repository administrators to be added as an authorised user within the repository. To get a GPG key, [download and install GPG](https://www.gnupg.org/download/) and then [generate your GPG key pair](https://www.gnupg.org/gph/en/manual/c14.html). Then provide your GPG key id to the authors.

Once given permission into the project and GPG key id added to the repository, update your local version of the repository by doing a `git pull` and then unlock the encrypted files/folders of the repository by running the following command on the terminal from within the project directory:

```bash
git-crypt unlock
```

The encrypted components of the repository will now be decrypted and accessible for running the workflow (described below).

### The workflow

The current workflow has the following steps:

```{r full-workflow, echo = FALSE, results = "asis"}
cat(
  c(
    "```mermaid",
    targets::tar_mermaid(
      targets_only = TRUE, outdated = FALSE, legend = FALSE, color = FALSE
    ),
    "```"
  ),
  sep = "\n"
)
```

To run the workflow, issue the following command in R from within the project directory

```R
targets::tar_make()
```

or issue the following command in Terminal from within the project directory

```bash
Rscript -e  "targets::tar_make()"
```

## Authors and Contributors

## Authors

* [Dr Minh Cong Tran](https://www.globalhealth.ox.ac.uk/our-researchers/minh-tran)
* [Dr Ernest Guevarra](https://ernest.guevarra.io)


## Contributors

* [Dr Aisha Adamu](https://www.tropicalmedicine.ox.ac.uk/team/aisha-adamu)
* [Dr Parinda Wattanasri](https://www.tropicalmedicine.ox.ac.uk/news/parinda-wattanasri-ihtm-2019-digital-vaccine-passports-in-thailand)
* [Dr Ainura Moldokmatova](https://www.tropicalmedicine.ox.ac.uk/team/ainura-moldokmatova)
* [Dr Chit Su Tinn](https://www.globalhealth.ox.ac.uk/our-researchers/chit-su-tinn)
* Dr Fona Qorina
* [Dr Proochista Ariana](https://www.ndm.ox.ac.uk/team/proochista-ariana)


## License

All code in this project is released under a [GPL-3.0](https://www.gnu.org/licenses/gpl-3.0.en.html#license-text) license. All text in this project is released under a [CC-BY-4.0](https://creativecommons.org/licenses/by/4.0/deed.en) license. All data is released under a [CC0](https://creativecommons.org/public-domain/cc0/) license.


## Citation

If you use the code, text, and/or data provided in this repository in your work/research, please cite this work using the suggested appropriate citation provided in [CITATION.cff](https://github.com/OxfordIHTM/stroke-lmic-review/blob/main/CITATION.cff).


## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/OxfordIHTM/stroke-lmic-review/issues). If you would like to contribute to the project, please see our [contributing guidelines](https://github.com/OxfordIHTM/stroke-lmic-review/blob/main/.github/CONTRIBUTING.md).

This project is released with a [Contributor Code of Conduct](https://github.com/OxfordIHTM/stroke-lmic-review/blob/main/.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
